---
title: "BoxOfficePrediction"
author: "MianchunLu, Yuting Gong, Guangxu Luo, Cijun Sun"
date: "March 7, 2019"
output: html_document
---

```{r warning=FALSE}
#Sys.setenv(JAVA_HOME='C:/Program Files/Java/jdk-11.0.2')
library(qdap) #text mining
library(stringr) #text mining
library(dplyr) #data manipulation
library(tidyr)
library(ggplot2) #visualization
library(corrplot) #visualization
library(cowplot) #visualization
library(wordcloud) #wordcloud
library(tidytext) #text mining
library(igraph)
library(Amelia)
library(lubridate)
library(reshape)
library(knitr)
library(tidyverse)
library(DT)

setwd('/Users/yutinggong/Desktop/Data/tmdb-box-office-prediction')
train=read.csv("train_raw.csv", stringsAsFactors = FALSE, na.strings = c("","#N/A","[]", 0))
test=read.csv("test_raw.csv", stringsAsFactors = FALSE,na.strings = c("","#N/A","[]", 0))
```

```{r}
colnames(train)[1]="id"
colnames(test)[1]="id"
```


```{r}
budget.name<- train$budget
genres.name <- train$numberOfGenres
ori.language<- train$original_language
ori.title <- train$original_title
popularity.name<- train$popularity
date.name<- train$release_date
runtime.name<- train$runtime
status.name <- train$status
```
# Step1: Exploratory Data Analysis
EDA helps us to understand the data better and gives us inspirations on how to clean, fix, reshape, rescale and combine data.

Train dataset has 3000 observations and 23 variables. Test dataset has 4398 observations and 22 variables. Firstly, we check out the type of each variables and examine the missing values.
```{r}
str(train)
```

```{r}
colnames(train)
colnames(test)
```

## Correlations between numeric variables and target revenue
```{r pressure}
#all numeric variables correlation map
numericVars <- which(sapply(train, is.numeric)) #index numeric variables
numericVarNames <- names(numericVars) #saving names vector for use later on
cat('There are', length(numericVars), 'numeric variables, which are', numericVarNames)
cor_numVar <- cor(train[,numericVars], use="pairwise.complete.obs") #correlations of all numeric variables
corrplot.mixed(cor_numVar, tl.col="black", tl.pos = "lt")
```

All numeric variables are positiviely correlated with revenue, especially budget and popularity have strong correlations.
So we will put special attention to these data's missing situation and fix any problems with them.

##EDA variable: original language
```{r }
#this frequency table show us the top ten most frequent languages of each movie
freq_terms(text.var = ori.language,top = 10)
#From this plot we can see the distribution of different languages.
plot(freq_terms(text.var=ori.language),top=10,stopwords = Top200Words)
```

English is the most frequently used language

## EDA variable: Revenue
Let's look at our target variable.
```{r warning= FALSE}
#{revenue} no missing value
sum(is.na(train$revenue))
ggplot(data=train,aes(x=revenue))+
  geom_histogram()+
  scale_x_continuous(labels = scales::comma)

count(train[train$revenue > 750000000,c('id','revenue')])
#some outliers (30 movies) have revenue over 750,000,000
#change the scale of the distribution so we can see the majority revenue clearly
ggplot(data=train,aes(x=revenue))+
  geom_histogram()+
  scale_x_continuous(labels=scales::comma, lim = c(0, 750000000))+
  scale_y_continuous(lim=c(0,600))

```

Revenue distribution has a VERY high skewness! Only 30 movies have revenue over 750,000,000, we scale the revenue to 0 to 750,000,000 so that we can see the distribution more clearly.
We transformed revenue data by using log:
```{r warning= FALSE}
ggplot(data=train,aes(x=log(revenue)))+
  geom_histogram()
```

This looks slightly better, more like a normal distribution.

##EDA variable: popularity
```{r }
#positive correlation between popularity and revenue(0.4614603)
cor(popularity.name,train$revenue)
#[graph]movie popularity and revenue
ggplot(data=train,aes(x=popularity.name,y=revenue))+
  geom_smooth()+geom_point()
```

At first the revenue rise as the popularity increase, but after the popularity increased to a certain degree, revenue begin to go down.

##EDA variable:overview
```{r}
#sentimental analysis for overview(chart)
train%>%
unnest_tokens(output = word, input = overview)%>%
inner_join(get_sentiments('nrc'))%>%
group_by(sentiment)%>%
count()%>%
ggplot(aes(x=reorder(sentiment,X = n),y=n,fill=sentiment))+geom_col()+guides(fill=F)+coord_flip()

#sentimental wordcloud for overview
wordcloudData = 
train%>%
unnest_tokens(output=word,input=overview)%>%
anti_join(stop_words)%>%
inner_join(get_sentiments('bing'))%>%
ungroup()%>%
count(sentiment,word,sort=T)%>%
spread(key=sentiment,value = n,fill=0)%>%
data.frame()
rownames(wordcloudData) = wordcloudData[,'word']
wordcloudData = wordcloudData[,c('positive','negative')]
set.seed(617)
comparison.cloud(term.matrix = wordcloudData,scale = c(2,0.5),max.words = 200, rot.per=0)
```


#Step2: Examine missing values
A lot of variables have missing values. We will look into them one by one and try to impute missing values. 
```{r}
colnames(train)[colSums(is.na(train)) > 0]
sum(is.na(budget.name)) #
sum(is.na(genres.name)) #
sum(is.na(ori.language))
sum(is.na(ori.title))
sum(is.na(train$overview))#
sum(is.na(train$popularity))
sum(is.na(train$production_companies))#
sum(is.na(train$production_countries))#
sum(is.na(train$release_date))
sum(is.na(train$runtime))#
sum(is.na(train$spoken_languages))#
sum(is.na(train$status))
sum(is.na(train$tagline))#
sum(is.na(train$title))
sum(is.na(train$Keywords))#
sum(is.na(train$cast))
sum(is.na(train$crew))#
sum(is.na(train$revenue))
```

We fill missing values for numeric data first: with the median. Sometimes mean can have some bias so the median could work better. We will deal with missing values in categorical variables later one by one.

```{r}
train$runtime[is.na(train$runtime)] <- median(train$runtime, na.rm= TRUE)
train$budget[is.na(train$budget)] <- median(train$budget, na.rm= TRUE)

test$runtime[is.na(test$runtime)] <- median(test$runtime, na.rm= TRUE)
test$budget[is.na(test$budget)] <- median(test$budget, na.rm= TRUE)

```

##variable: title
3 missing titles in test data. we will fill them with original_titles
```{r}
test$title[is.na(test$title)] = test$original_title[is.na(test$title)]
```


#Step 3: Fix data types: release_date
Release_date is in weird format of M/D/Y.
```{r }
sum(is.na(train$release_date)) #check missing value
sum(is.na(test$release_date))
#check if year all in 2 digits format. if the last 3rd character of all observations is "/", it proves year all in 2 digits. 
```
There is no missing value in release_date in train. One date is missing in test. 
It is in string format. However, the format is wrong because Years in the release_date only has 2 digits, and some days and months are in 2 digits, and some have 1 digit.
We are going to mannualy search the release_date for the missing data, and then fix the release_date's format and data type.
```{r }
test[is.na(test$release_date),]$release_date="5/1/00"
```

```{r }
#use separate to get month, day, year information
train=separate(data =train, col=release_date,into=c("month", "day", "year"), sep = '/')
train$month<-as.numeric(train$month)
train$day <-as.numeric(train$day)
train$year<- as.numeric(train$year)
#fill release_year to 4 digits
train[train$year>19,]$year <- train[train$year>19,]$year + 1900
train[train$year<=19,]$year <- train[train$year<=19,]$year + 2000
#fill month to 2 digits
train[train$month<=9,]$month<-paste("0",train[train$month<=9,]$month,sep="")
#fill day to 2 digits
train[train$day<=9,]$day<-paste("0",train[train$day<=9,]$day,sep="")
#replace release_date column with new date information
train$release_date=paste(train$year,train$month,train$day,sep="-")
```
same work on test data:
```{r }
test=separate(data =test, col=release_date,into=c("month", "day", "year"), sep = '/')
test$month<-as.numeric(test$month)
test$day <-as.numeric(test$day)
test$year<- as.numeric(test$year)
#fill release_year to 4 digits
test[test$year>19,]$year <- test[test$year>19,]$year + 1900
test[test$year<=19,]$year <- test[test$year<=19,]$year + 2000
#fill month to 2 digits
test[test$month<=9,]$month<-paste("0",test[test$month<=9,]$month,sep="")
#fill day to 2 digits
test[test$day<=9,]$day<-paste("0",test[test$day<=9,]$day,sep="")
#replace release_date column with new date information
test$release_date=paste(test$year,test$month,test$day,sep="-")
```
Great! release_date is now in the right format. 
We will add one more feature engeering based to check the week of the day based on date info:
```{r }
#check which day of the week
train$week_day = weekdays(as.Date(train$release_date))
train$month<-as.numeric(train$month)
train$day <-as.numeric(train$day)
train$year<- as.numeric(train$year)

test$week_day = weekdays(as.Date(test$release_date))
test$month<-as.numeric(test$month)
test$day <-as.numeric(test$day)
test$year<- as.numeric(test$year)

#[graph]movie count by week of the day
plot1<-train %>%
  select(id,week_day,revenue)%>%
  group_by(week_day)%>%
  ggplot(aes(x=week_day))+
  geom_bar()+
  scale_x_discrete(limits=c("Monday","Tuesday","Wednesday","Thursday", "Friday","Saturday","Sunday"))+
  theme(axis.text.x = element_text(angle = 60, hjust = 1))
plot2<-
  train %>%
  select(id,week_day,revenue)%>%
  group_by(week_day)%>%
  summarize(mean_revenue=mean(revenue))%>%
  ggplot(aes(x=week_day,y=mean_revenue))+
  geom_bar(stat="identity")+
  scale_x_discrete(limits=c("Monday","Tuesday","Wednesday","Thursday", "Friday","Saturday","Sunday"))+
  theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  scale_y_continuous(labels = scales::comma)

plot_grid(plot1, plot2,labels = "AUTO")
```
Most movie are released on Fridays. 
However, the average movie revenue is the highest on Wednesdays instead of Fridays. Interesting!

year and revenue; month and revenue
```{r }
#[graph]movie release count by year
plot3<-train %>%
   select(year)%>%
  group_by(year)%>%
  ggplot(aes(x=year))+
  geom_bar()

#[graph]movie release count by month
plot4<-train %>%
  select(month)%>%
  group_by(month)%>%
  ggplot(aes(x=month))+
  geom_bar()
  scale_x_discrete(limits=c("1","2","3","4","5","6","7","8","9","10","11","12"))

plot_grid(plot3, plot4,labels = "AUTO")

```

```{r }
#[graph]movie release year and revenue
plot5<-train%>%
  select(year, revenue)%>%
  group_by(year)%>%
  summarize(mean_revenue=mean(revenue))%>%
  ggplot(aes(x=year, y=mean_revenue))+
  geom_line()
#positive correlation between release year and revenue(0.1379329)
cor(train$year,train$revenue)
cor.test(train$year, train$revenue)

#[graph]movie release month and revenue
plot6<- train%>%
  select(month, revenue)%>%
  group_by(month)%>%
  summarize(mean_revenue=mean(revenue))%>%
  ggplot(aes(x=month, y=mean_revenue))+
  geom_line()

plot_grid(plot5, plot6,labels = "AUTO")

#correlation between release month and mean revenue is not strong or obvious
cor(train$month,train$revenue)
cor.test(train$month, train$revenue)

```

There is a positive correlation between release year and revenue(0.1379329). The relationship between month and revenue is unclear. 
Extracting Values with Regular Expressions--"belongs_to_collection"


#Step4: Dealing with strings in JSON format to get new useful variables
##variable: belongs_to_collection
We will transform variable "belongs_to_collection" because it contains a lot of information in one column including collection id, collection name, poster_path and backdrop_path. We assume that whether a movie belongs to a collection will influence its revenue. So we extract information from the string, and create two variables "collection_id" and "collection_name".
```{r}
library(stringr)
train$collection_id <- str_extract(train$belongs_to_collection, "(?<=id\\'\\:\\s{1})\\d{1,}")
train$collection_name <- str_extract(train$belongs_to_collection, "(?<=name\\'\\:\\s{1}\\').+(?=\\'\\,\\s{1}\\'poster)")
```

The new added two variables have lots of missing values.
```{r}
sum(is.na(train$collection_id))
sum(is.na(train$collection_name))
```
Variable "collection_id" has more NAs.To check if there is error during the extracting process, I find out all the collection ids without names. 
```{r}
train[which(is.na(train$collection_name)&!is.na(train$collection_id)),"collection_id"]
```

I find that there is a problem of the regular expression. Some collection names are not in the standard format. I will revise the regular expression and re-run the step 2.
```{r}
train[which(train$collection_id=="91746"),"belongs_to_collection"]
```

```{r}
train$collection_id <- str_extract(train$belongs_to_collection, "(?<=id\\'\\:\\s{1})\\d{1,}")
train$collection_name <- str_extract(train$belongs_to_collection, "(?<=name\\'\\:\\s{1}).+(?=\\,\\s{1}\\'poster)")
sum(is.na(train$collection_id))
sum(is.na(train$collection_name))
```

Then, I am going to compare the average revenue of movies that are in collections and the average revenue of others.
Based on the following graph, there is a huge gap of the mean revenue between in-collection movies and not-in-collection movies.
```{r}
collection <- train[!is.na(train$belongs_to_collection),]%>%
  summarise(med = round(mean(revenue) / 1000000, digits = 0))
  
noCollection <- train[is.na(train$belongs_to_collection),] %>%
  summarise(med = round(mean(revenue) / 1000000, digits = 0))
  
means <- rbind(collection, noCollection)

means <- cbind(c("In Collection", "No Collection"), means)

colnames(means) <- c("collection", "mean")

library(ggplot2)
ggplot(means, aes(x = collection, y = mean, fill = collection)) +
  geom_bar(stat = "identity", color = "black", alpha = 0.8)+
  theme_light() +
  xlab("") +
  ylab("Millions of dollars") +
  ggtitle("Median Box Office Revenue For Movies\nIn Collections And Not In Collections") +
  theme(legend.position="none")
```

Now I will drop the "collection_id" and "collection_name", and convert the values in the belongs_to_collection column from strings to a numerical value of 1 (is in a collection) and 0 (is not). 
```{r}
drop_collection=c("collection_id","collection_name")
train[,drop_collection]<-list(NULL)
train$belongs_to_collection<-ifelse(is.na(train$belongs_to_collection),0,1)
test$belongs_to_collection<-ifelse(is.na(test$belongs_to_collection),0,1)

```


##variable:genres
Extracting Values with Regular Expressions--"genres"
The purpose of this part is to see if the numbers of genres and the types of genres can influence the revenue. Firstly, I will count the number of genres of each movie, and then I will create several new variables to reshape the information related to genres.
```{r}
library(ggplot2)
genreCount <-  ifelse(is.na(train$genres),0,str_count(train$genres, "\\}")) # each genre is followed by a "}"
train$numberOfGenres <- genreCount
numberOfSplitCols <- max(na.omit(genreCount))  # to find out the max number of genres of a single movie, the result is 7

genreCount %>%
  as.data.frame(stringsAsFactors = F) %>%     # convert genreCount (a vector) into a data frame
  ggplot(aes(genreCount)) +
  geom_histogram(stat = "count",
                 fill="orange",
                 color = "black",
                 alpha = 0.85) +
  scale_x_discrete(limits=0:numberOfSplitCols) +
  theme_light() +
  xlab("Number Of Genres Per Movie") +
  ylab("Number Of Movies") +
  ggtitle("Histogram Of Number Of Genres Per Movie")  # seven movies have 0 genres
```
Train dataset has 7 observations with NA for "genres", and test dataset has 16 NAs.
```{r}
sum(is.na(train$genres))
sum(is.na(test$genres))
train%>%
  filter(is.na(numberOfGenres))%>%
  count()
```

```{r}
genresSplit <- as.data.frame(str_split_fixed(train$genres, "\\}\\,\\s\\{", numberOfSplitCols), stringsAsFactors = F)

genreIds <- as.data.frame(sapply(genresSplit, function(x) str_extract(x, "(?<=id\\'\\:\\s{1})\\d{1,}")), stringsAsFactors = F)
genreIds <- as.data.frame(sapply(genreIds, function(x) as.numeric(x)), stringsAsFactors = F)
genreIds[is.na(genreIds)] <- ""

genreNames <- as.data.frame(sapply(genresSplit, function(x) str_extract(x, "(?<=name\\'\\:\\s{1}\\').+(?=\\')")), stringsAsFactors = F)
genreNames[is.na(genreNames)] <- ""

# break up the table to find out the most common genre in the dataset
gs <- as.data.frame(table(unlist(genreNames)), stringsAsFactors = F)
gs <- gs[2:nrow(gs),]  # drop the ""

# there are 20 different tags of genres
ggplot(data=gs, aes(x = reorder(Var1, Freq),
             y = Freq,
             fill = Var1)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  theme_light() +
  xlab("") +
  ylab("Number Of Movies") +
  ggtitle("Number of Movies Containing Specific Tag") +
  theme(legend.position="none")
```

Now I will convert the information in the genres column to 20 numerical variables, value of 1 (is in this genre) and 0 (is not). Same conduction has been done to test dataset. I will also drop "genres".
```{r}
library(plyr)
n=nrow(gs)
for (i in 1:n)
{
  train$i=grepl(as.character(gs$Var1[i]),train$genres, ignore.case = T)
  train$i[train$i==TRUE]=1
  train$i[train$i==FALSE]=0
  a=as.character(gs$Var1[i])
  train=rename(train,c(i=a))
}
  
genreCount_test <- str_count(test$genres, "\\}")  # each genre is followed by a "}"
test$numberOfGenres <- genreCount_test
test$numberOfGenres[is.na(test$genres)] <- 0
numberOfSplitCols_test <- max(na.omit(genreCount_test))  # to find out the max number of genres of a single movie, the result is 8

for (i in 1:n)
{
  test$i=grepl(as.character(gs$Var1[i]),test$genres, ignore.case = T)
  test$i[test$i==TRUE]=1
  test$i[test$i==FALSE]=0
  a=as.character(gs$Var1[i])
  test=rename(test,c(i=a))
}

train[,"genres"]<-list(NULL)
test[,"genres"]<-list(NULL)
```


##dealing with missing value: filling in the missing value of genres.
```{r}
train[which(train$"id"==1815),"Comedy"]=1
train[which(train$"id"==2424),"Drama"]=1
train[which(train$"id"==2424),"Action"]=1
train[which(train$"id"==471),"Drama"]=1
train[which(train$"id"==471),"Adventure"]=1
train[which(train$"id"==2687),"Drama"]=1
train[which(train$"id"==2687),"Crime"]=1
train[which(train$"id"==2687),"Thriller"]=1
train[which(train$"id"==1820),"Drama"]=1
train[which(train$"id"==1820),"Romance"]=1
train[which(train$"id"==2901),"Fantasy"]=1
train[which(train$"id"==2901),"Drama"]=1
train[which(train$"id"==1623),"Thriller"]=1
train[which(train$"id"==1623),"Comedy"]=1

test[which(test$"id"==3074),"Thriller"]=1
test[which(test$"id"==3074),"Drama"]=1
test[which(test$"id"==3794),"Drama"]=1
test[which(test$"id"==3911),"Drama"]=1
test[which(test$"id"==4222),"Drama"]=1
test[which(test$"id"==4222),"Action"]=1
test[which(test$"id"==4443),"Drama"]=1
test[which(test$"id"==4616),"Comedy"]=1
test[which(test$"id"==4965),"Action"]=1
test[which(test$"id"==5063),"Drama"]=1
test[which(test$"id"==5063),"Crime"]=1
test[which(test$"id"==5119),"Drama"]=1
test[which(test$"id"==5214),"Documentary"]=1
test[which(test$"id"==5214),"Family"]=1
test[which(test$"id"==5252),"Comedy"]=1
test[which(test$"id"==5520),"Mystery"]=1
test[which(test$"id"==5520),"Comedy"]=1
test[which(test$"id"==5520),"Crime"]=1
test[which(test$"id"==6450),"Drama"]=1
test[which(test$"id"==6450),"Comedy"]=1
test[which(test$"id"==6486),"Comedy"]=1
test[which(test$"id"==6565),"Documentary"]=1
test[which(test$"id"==6818),"Drama"]=1



```

##variable: "cast" and "crew"
The purpose of this part is to see if the numbers of casts and crews can influence the revenue. Firstly, I will count the number of casts and crews of each movie, and then I will create several new variables to reshape the information related to casts and crews.
```{r}
castCount <- str_count(train$cast, "\\}")  # each genre is followed by a "}"
train$numberOfcasts <- castCount
train$numberOfcasts[is.na(train$numberOfcasts)] <- 0
MaxNumberOfcasts <- max(na.omit(castCount))  # to find out the max number of casts of a single movie, the result is 156

castCount_test <- str_count(test$cast, "\\}")  # each genre is followed by a "}"
test$numberOfcasts <- castCount_test
test$numberOfcasts[is.na(test$numberOfcasts)] <- 0
MaxNumberOfcasts_test <- max(na.omit(castCount_test))  # to find out the max number of casts of a single movie, the result is 165

```


```{r}
train%>%
  ggplot(aes(x=numberOfcasts, y=revenue))+
  geom_point(color="orange")+
  geom_smooth(method = lm)+
  xlab("Number Of Casts") +
  ylab("Revenue") +
  ggtitle("Revenue depending on number of casts")
```

The observations that have error in the "cast" variable.
```{r}
sum(is.na(train$cast))
sum(is.na(test$cast))
```

```{r}
crewCount <- str_count(train$crew, "\\}")  # each genre is followed by a "}"
train$numberOfcrews <- crewCount
train$numberOfcrews[is.na(train$crew)]<-0
MaxNumberOfcrew <- max(na.omit(crewCount))  # to find out the max number of casts of a single movie, the result is 194

crewCount_test <- str_count(test$crew, "\\}")  # each genre is followed by a "}"
test$numberOfcrews <- crewCount_test
test$numberOfcrews[is.na(test$crew)]<-0
MaxNumberOfcrew_test <- max(na.omit(crewCount_test))  # to find out the max number of casts of a single movie, the result is 182
```

```{r}
train%>%
  ggplot(aes(x=numberOfcrews, y=revenue))+
  geom_point(color="orange")+
  geom_smooth(method = lm)+
  xlab("Number Of Crews") +
  ylab("Revenue") +
  ggtitle("Revenue depending on number of crews")
```

##variable: production_companies
Extracting Values with Regular Expressions--"production_companies"
The purpose of this step is to find out the influence of the number of production companies, and whether the movie was producted by big name companies.
Firstly, I count the number of production companies of each movie.
Secondly, I select the companies that have produced more than 50 movies, and create 11 new variables to show if the movie was produced by these companies.
```{r}
companyCount <- str_count(train$production_companies, "\\}")  
train$numberOfcompanies <- companyCount
train$numberOfcompanies[is.na(train$production_companies)]<- 0
companyCount_test <- str_count(test$production_companies, "\\}")  
test$numberOfcompanies <- companyCount_test
test$numberOfcompanies[is.na(test$production_companies)]<- 0
summary(companyCount)
summary(companyCount_test)
```

```{r}
companySplit <- as.data.frame(str_split_fixed(train$production_companies, "\\}\\,\\s\\{", companyCount), stringsAsFactors = F)

companyIds <- as.data.frame(sapply(companySplit, function(x) str_extract(x, "(?<=id\\'\\:\\s{1})\\d{1,}")), stringsAsFactors = F)
companyIds <- as.data.frame(sapply(companyIds, function(x) as.numeric(x)), stringsAsFactors = F)
companyIds[is.na(companyIds)] <- ""

companyNames <- as.data.frame(sapply(companySplit, function(x) str_extract(x, "(?<=name\\'\\:\\s{1}\\').+(?=\\'\\,)")), stringsAsFactors = F)
companyNames[is.na(companyNames)] <- ""

# break up the table to find out the most common production companies in the dataset
pcs <- as.data.frame(table(unlist(companyNames)), stringsAsFactors = F)
pcs <- pcs[2:nrow(pcs),]  # drop the ""

summary(pcs$Freq)

# there are 3668 different tags of production companies, and I will select the companies that has produced more than 50 and 100 movies.
pcs_top11=pcs%>%filter(Freq>=50)
ggplot(data=pcs_top11, aes(x = reorder(Var1, Freq),
             y = Freq,
             fill = Var1)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  theme_light() +
  xlab("") +
  ylab("Production Companies Of Movies") +
  ggtitle("Number of Movies Produced by top 11 companies(produced more than 50 movies)") +
  theme(legend.position="none")

pcs_top4=pcs%>%filter(Freq>=100)
ggplot(data=pcs_top4, aes(x = reorder(Var1, Freq),
             y = Freq,
             fill = Var1)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  theme_light() +
  xlab("") +
  ylab("Production Companies Of Movies") +
  ggtitle("Number of Movies Produced by top 4 companies(produced more than 100 movies)") +
  theme(legend.position="none")
```

```{r}
n=nrow(pcs_top11)
for (i in 1:n)
{
  train$i=grepl(as.character(pcs_top11$Var1[i]),train$production_companies, ignore.case = T)
  train$i[train$i==TRUE]=1
  train$i[train$i==FALSE]=0
  a=as.character(pcs_top11$Var1[i])
  train=rename(train,c(i=a))
}
  
for (i in 1:n)
{
  test$i=grepl(as.character(pcs_top11$Var1[i]),test$production_companies, ignore.case = T)
  test$i[test$i==TRUE]=1
  test$i[test$i==FALSE]=0
  a=as.character(pcs_top11$Var1[i])
  test=rename(test,c(i=a))
}
```

##variable: production_countries
Extracting Values with Regular Expressions--"production_countries"
Creating a new varibale to show how many countries each movie was produced in.
```{r}
countriesCount <- str_count(train$production_countries, "\\}")  
train$numberOfcoun <- countriesCount
train$numberOfcoun[is.na(train$production_countries)]<-0

countriesCount_test <- str_count(test$production_countries, "\\}")  
test$numberOfcoun <- countriesCount_test
test$numberOfcoun[is.na(test$production_countries)]<-0

summary(countriesCount)
summary(countriesCount_test)
```


##variable: "spoken_languages"
Extracting Values with Regular Expressions--"spoken_languages"
Creating a new varibale to show how many different languages each movie was produced in.
```{r}
lanCount <- str_count(train$spoken_languages, "\\}")  
train$numberOflang <- lanCount
train$numberOflang[is.na(train$spoken_languages)] <- 0
summary(train$numberOflang)

lanCount_test <- str_count(test$spoken_languages, "\\}")  
test$numberOflang <- lanCount_test
test$numberOflang[is.na(test$spoken_languages)] <- 0

summary(lanCount)
summary(lanCount_test)
```
Some movies have more than 1 language. Does more languages lead to more revenue?
No correlation is observed. We will drop this variable. 

##variable: status
As for variable "status", there are two levels in train dataset, however, 4 levels in test dataset. Variance of levels will negatively influence the predictive model. Thus, I create a new variable with only two levels, is released(1) and not released(0).
```{r}
train$status=as.factor(train$status)
levels(train$status)
test$status=as.factor(test$status)
levels(test$status)

train$is_released[train$status=="Released"]=1
train$is_released[train$status!="Released"]=0
count(train$is_released==0)

test$is_released[test$status=="Released"]=1
test$is_released[test$status!="Released"| is.na(test$status)]=0
count(test$is_released==0)
```


#Step 5: Rescaling variables
Normalization and Standardization:
In this dataset, there are various numeric variables that will influence the movies' revenue. However, these variables scale from single digits to millions. The coefficient of variables in lower scale, such as popularity, will be covered by the coefficient of variables in higher scale, such as budget.Therefore, in this step, I am going to normalize and standardize all the numeric variables using z-score scaling.
```{r}
train$budget2=scale(train$budget,center=T,scale=T) 
train$popularity2=scale(train$popularity,center=T,scale=T) 
train$runtime2=scale(train$runtime,center=T,scale=T) 
train$numberOfGenres2=scale(train$numberOfGenres,center=T,scale=T) 
train$numberOfcasts2=scale(train$numberOfcasts,center=T,scale=T) 
train$numberOfcrews2=scale(train$numberOfcrews,center=T,scale=T) 
train$numberOfcompanies2=scale(train$numberOfcompanies,center=T,scale=T) 
train$numberOflang2=scale(train$numberOflang,center=T,scale=T) 
train$numberOfcoun2=scale(train$numberOfcoun,center=T,scale=T) 

train$revenue2=scale(train$revenue,center=T,scale=T) 

test$budget2=scale(test$budget,center=T,scale=T) 
test$popularity2=scale(test$popularity,center=T,scale=T) 
test$runtime2=scale(test$runtime,center=T,scale=T) 
test$numberOfGenres2=scale(test$numberOfGenres,center=T,scale=T) 
test$numberOfcasts2=scale(test$numberOfcasts,center=T,scale=T) 
test$numberOfcrews2=scale(test$numberOfcrews,center=T,scale=T) 
test$numberOfcompanies2=scale(test$numberOfcompanies,center=T,scale=T) 
test$numberOflang2=scale(test$numberOflang,center=T,scale=T) 
test$numberOfcoun2=scale(test$numberOfcoun,center=T,scale=T)
```


#Step 6: Dropping variables
Remove irrelevant variables from the dataset: "homepage", "imdb_id", "original_title", "poster_path". For some variables, we have created useful new data already so we will also drop original variables. We will also drop variables that we don't have proper methods to retrieve information yet, such as "cast".
```{r}
drop_var=c("homepage", "imdb_id","poster_path")
train[,drop_var] <- list(NULL)
test[,drop_var] <- list(NULL)
train[,"genres"]<-list(NULL)
test[,"genres"]<-list(NULL)
drop_var2=c("production_companies","production_countries","spoken_languages","status","crew","keywords", "cast","day") 
train[,drop_var2]<-list(NULL)
test[,drop_var2]<-list(NULL)
```

After cleaning, now we don't have any missing values in numeric values. We only have missing values in string variables "overview","tagline" and "Keywords", which is fine, because we cannot immpute string, and we will conduct sentiment analysis on them in the future in project 2. 
```{r}
colnames(train)[colSums(is.na(train)) > 0]
colnames(test)[colSums(is.na(test)) > 0]
```


```{r}
write.csv(train,file="train_clean.csv")
write.csv(test,file="test_clean.csv")
```
